---
title: "Puzzle Report"
author: "Steve Tamayo"
date: "2023-09-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(dplyr)
library(foreach)

library(wordcloud)
library(RColorBrewer)
```

## Where the data came from
I found a dataset on kaggle called <a href="https://www.kaggle.com/datasets/rtatman/english-word-frequency">"English Word Frequency"</a>. The data set is 6 years old, but it will do for now. 

From the description:
"This dataset contains the counts of the 333,333 most commonly-used single words on the English language web, as derived from the Google Web Trillion Word Corpus."
 
```{r load and clean data}
words_raw <- read_csv("unigram_freq.csv")
words_clean <- na.omit(words_raw)
```

## What letters I have so far
I have guessed the letters "e" and "o". The hope was to use vowels to help whittle the options down. 

## Code

### Functions
These functions help create the regex based on the letters I already used and where they appear (and don't appear) in words.
```{r}
rdl_revealed_letters = "[^eo]"

createRegex = function(input_conditions){
  tmp_word = c(rep("",length(input_conditions)))
  # tmp_unique = paste(c(
  #   "[^",
  #   paste(unique(input_conditions[nzchar(input_conditions)]),collapse = ''),
  #   "]"
  #   ),collapse = '')
  tmp_unique = rdl_revealed_letters
  foreach(i = 1:length(input_conditions)) %do% {
    tmp_word[i] <- ifelse(input_conditions[i]!="",
                          paste(c(
                            "[",
                            input_conditions[i],
                            "]"),collapse = ''),
                          tmp_unique)
  }
  return <- paste(tmp_word,collapse = '')
}

createDFPos = function(input_condition){
  return <-data.frame(subset(words_clean,grepl(createRegex(input_condition),word) & nchar(word, keepNA=FALSE)==length(input_condition)))

}
```

### Creating Conditions for each word
```{r}
#Riddle Words conditions
rdl_sen1word1_con = c("o","","","e","","") #6 letters, 1 character = O, 4 character = e
rdl_sen1word2_con = c("","","o","","","")
rdl_sen1word3_con = c("","e")
rdl_sen1word4_con = c("","","","","","")
rdl_sen1word5_con = c("","","","")
rdl_sen1word6_con = c("","")
rdl_sen1word7_con = c("","e","","")

rdl_sen2word1_con = c("o","")
rdl_sen2word2_con = c("","o")
rdl_sen2word3_con = c("","","","","")
rdl_sen2word4_con = c("","","","")

rdl_sen3word1_con = c("","","","o","","","","e")
rdl_sen3word2_con = c("","e","")
rdl_sen3word3_con = c("","")
rdl_sen3word4_con = c("","o")
rdl_sen3word5_con = c("","","","o","","","","e")
rdl_sen3word6_con = c("","","","","o","")
rdl_sen3word7_con = c("","")
rdl_sen3word8_con = c("","o","")
```

### Creating data frames for each word
```{r}
df_sen1word1 <- createDFPos(rdl_sen1word1_con)
df_sen1word2 <- createDFPos(rdl_sen1word2_con)
df_sen1word3 <- createDFPos(rdl_sen1word3_con)
df_sen1word4 <- createDFPos(rdl_sen1word4_con)
df_sen1word5 <- createDFPos(rdl_sen1word5_con)
df_sen1word6 <- createDFPos(rdl_sen1word6_con)
df_sen1word7 <- createDFPos(rdl_sen1word7_con)

df_sen2word1 <- createDFPos(rdl_sen2word1_con)
df_sen2word2 <- createDFPos(rdl_sen2word2_con)
df_sen2word3 <- createDFPos(rdl_sen2word3_con)
df_sen2word4 <- createDFPos(rdl_sen2word4_con)

df_sen3word1 <- createDFPos(rdl_sen3word1_con)
df_sen3word2 <- createDFPos(rdl_sen3word2_con)
df_sen3word3 <- createDFPos(rdl_sen3word3_con)
df_sen3word4 <- createDFPos(rdl_sen3word4_con)
df_sen3word5 <- createDFPos(rdl_sen3word5_con)
df_sen3word6 <- createDFPos(rdl_sen3word6_con)
df_sen3word7 <- createDFPos(rdl_sen3word7_con)
df_sen3word8 <- createDFPos(rdl_sen3word8_con)
```

## Word Clouds
I hope that word clouds would help me visually see what words might go together.

```{r, echo=FALSE}

set.seed(1234) # for reproducibility 


wordcloud(words = df_sen1word1$word, freq = df_sen1word1$count, min.freq = 100,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))

wordcloud(words = df_sen1word2$word, freq = df_sen1word2$count, min.freq = 10000,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))

wordcloud(words = df_sen1word3$word, freq = df_sen1word3$count, min.freq = 100,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))

wordcloud(words = df_sen1word4$word, freq = df_sen1word4$count, min.freq = 100,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"),
          scale=c(4,0.25) )

wordcloud(words = df_sen1word5$word, freq = df_sen1word5$count, min.freq = 100,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"),
          scale=c(5,0.25) )

wordcloud(words = df_sen1word6$word, freq = df_sen1word6$count, min.freq = 100,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"),
          scale=c(5,0.25) )

wordcloud(words = df_sen1word7$word, freq = df_sen1word7$count, min.freq = 100,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"),
          scale=c(5,0.25) )


```

